### 2010-12-04 docs/tex/review.tex
References fixed.
Unfinished Artificial Life section

@@

@@

The field of Artificial Life (AL) has been described by Taylor as a tool for biological inquiry \cite{taylor1993}. While providing a brief survey over different AL models he talks about \textbf{wetware systems} which work at the molecular level, the \textbf{software systems} which work at the cellular level and the \textbf{hardware systems} which works at the organism level.

@@

\subsubsection{Echo}

>>>>

\section{Introduction}

@@

Christopher G. Langton is considered as one of the founders of the filed of Artificial Life. He invented the term in the late 1980's when he organized the first ``International Conference on the Synthesis and Simulation of Living Systems" at the Los Alamos National Laboratory in 1987.

@@

The field of Artificial Life (AL) has been described by Taylor as a tool for biological inquiry \cite{taylor1993}. While providing a brief survey over different AL models he talks about \textbf{Wetware systems} which work at the molecular level, the \textbf{Software systems} which work at the cellular level and the \textbf{Hardware systems} which works at the organism level.

%Describe Wetware, Software and Hardware systems of artificial life.

@@

\subsection{Echo}
Echo is a gedanken experiment rather than a precise simulation.

\subsubsection{Criteria}
Echo has been constructed on a certain set of criteria. The following is a short summary on it extracted from \cite{holland1996}.

\begin{itemize}
	\item Simplicity is considered as the first and foremost criteria. Instead of emulating a real system Echo is more of a thought experiment. Simplicity is attained by carefully constraining agent interaction and also giving the agents only a primitive internal model. 
	\item Actions and interaction of each agent in echo has been designed to be part of a wide range of \textsl{CAS} setting, while mobility is also part of a wide range of geographical setting. Input to the environment which are considered as stimuli or resource can also be diversified. 
	\item Fitness of each of the agents is an evolving criteria. Instead of considering fitness as an external exogenous factor, it should be dependent on the context provided by the site and other agents. Instead of being a constant value it should evolve along with the system. 
	\item ``The primitive mechanisms in Echo should have ready counter parts in all \textsl{CAS}. Interpretation of results from the Echo model should be direct and ready-made. As simulation is nothing but manipulation of numbers and symbols, it is always possible to make fanciful and deceiving interpretation of them, taking the opportunity to prove one's point. So by applying primitive mechanism for interpretation it is possible to avoid misinterpretation. 5
	\item 
	\item 
\end{itemize}

\subsubsection{Organization}

\subsubsection{Agents}
Individual agents in echo

\subsubsection{Replication}

\subsubsection{Interactions}
\paragraph{Combat}
\paragraph{Trading}
\paragraph{Mating}
\subsubsection{Results}

\paragraph{Criteria}
